Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis and First-guess

### 2022-04-11 analysis/chapters/paper_ana_20181122.tex
new version of paper

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales\corref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{Victoria Galligani}

@@

  \begin{abstract}
  In this paper we evaluate the impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed over central and north-eastern Argentina during November 22, 2018. The accumulated precipitation associated with this MCS was quite high, exceeding 200 mm over northern Argentina and Paraguay. This MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during November 2018.

  We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-members ensemble initialized from the deterministic GFS run adding random perturbations with climatological covariance. A multiphysics approach was also used to represent model errors, using different physics configurations (a combination of PBL and convection parameterizations). We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP's prepBUFR files, AUT combining CONV and dense automatic surface weather station networks, SATWND, combining AUT with satellite-derived winds and RAD, including SATWND and satellite radiances from different microwave and infrared sensors (AMSU, HIRS, MHS, ATMS, AIRS, and IASI). We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation.
  \end{abstract}
   \begin{keyword} Regional Data Assimilation, Surface Obsevations, Satellite Observations\end{keyword}
 \end{frontmatter}

@@

Severe weather events cause significant human and material losses around the world. A large number of these phenomena are associated with the occurrence of deep moist convection including tornadoes, intense wind gusts, extreme precipitation in short time periods, large hail, and lightning.
Southern South America has been shown to have the highest frequency of favorable conditions for high-impact meteorological events (Brooks et al., 2003) and the highest occurrence of large hail events (Cecil and Blankenship, 2012).
This is also confirmed by observational evidence and high impact weather reports (Matsudo et al., 2015; Rasmussen et al., 2014).

Forecasting mesoscale meteorological phenomena and particularly deep moist convection is a scientific and technological challenge due to several factors.
On the one hand, mesoscale phenomena have limited predictability, while on the other hand, there is great difficulty in diagnosing the state of the atmosphere at small spatial and short temporal scales (for example from 1 to 10 kilometers and in the order of minutes).
To solve this problem, data assimilation (DA) at the mesoscale is a topic that has gained increasing interest since it can provide appropriate initial conditions for the initialization of high-resolution forecasts (Sun et al., 2014).

DA methods can successfully be implemented by using observations with sufficient temporal and spatial resolution to characterize mesoscale atmospheric circulations.
The assimilation of conventional observations from surface stations has an important role in improving the initial conditions that lead to better forecasts.
For example, Ha and Snyder (2014) showed that the assimilation of temperature and dew point temperature systematically improved the structure of the simulated planetary boundary layer that subsequently resulted in a better precipitation forecast over the U.S.
However, surface observations, which directly measure the atmospheric state, have limited availability in South America. Given the sparsity of the local conventional observing network, it is important to explore the potential benefits of including additional sources of observations at a regional scale.
Other types of observations are being assimilated with relatively high spatial and temporal resolution, such as satellite radiance observations or retrieval products.
Previous work has shown a positive impact at incorporating temperature and humidity profiles derived from the multispectral infrared sensors (i.e.~AIRS and IASI) in a regional domain application.
Miyoshi and Kunii (2012) assimilated observations, atmospheric temperature, and humidity profile data from the AIRS and found improvement on the tracking of two typhoons near Japan.
Dillon et al. (2019) also assimilated retrievals from the AIRS sensor and reported improvements on the thermodynamic variables and the regional circulation over Southern South America.

However radiance observations are indirect measurements and are more difficult to incorporate into DA systems as they require complex forward models. Moreover, Bao et al. (2015) studied the impact on temperature and humidity forecast over the western USA while assimilating microwave and infrared radiance data and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. Recently Zhu et al. (2019) studied the impact of assimilating satellite radiance data within a frequently updated regional system and showed an improvement for all variables, in particular for relative humidity at upper levels.
Satellite-derived winds from water vapor channels and cloud drift motion vectors also have an overall positive impact on analysis and short-range forecasts (Gao et al., 2015).

Having analyses with higher temporal resolution than those available from global forecasting systems (e.g.~at hourly or sub-hourly) and using an increased number of regional observations that are not assimilated in global DA systems are some of the advantages of regional DA.
Previous work has shown promising results on mesoscale DA in the region using different approaches such as LETKF; (Dillon et al., n.d., 2016) and 3D-Var (gustavo Goncalves de Goncalves et al., 2015).
In particular, the use of ensemble-based methods has shown great potential for data assimilation in these scales, as they are able to characterize the flow-dependent evolution of the background error covariances.
Moreover, the use of ensembles also provides valuable information about the uncertainties in the forecast.
Recently a rapid-refresh ensemble-based DA system has been experimentally implemented during the Remote sensing of Electrification, Lightning, And Mesoscale/microscale Processes with Adaptive Ground Observations (RELAMPAGO) Field Campaign (central Argentina, November-December 2018, Nesbitt et al. (2021)) with promising results (Dillon et al., n.d.).
This system assimilated data from high-resolution surface networks, AMDAR data from local aircraft flights, soundings, AIRS retrievals, high-resolution GOES-16 wind estimates, and local radar data every hour with a grid spacing of 10 km.
The forecast initialized from the analyses shows an overall similar performance to cold-start initializations from the Global Forecast System analysis, and even a positive impact in some cases.

One important challenge of regional data assimilation systems is the assessment of their representation of the true atmospheric state and the skill of the forecasts initialized using their analysis as initial conditions.
In this sense, the observations and measurements taken during the intense observing period of RELAMPAGO are an invaluable resource to validate a regional data assimilation system.

The main objective of this work is to evaluate the impact of different observation types, including frequent surface observations, satellite-derived winds, and clear-sky satellite radiances from different platforms, into a regional frequent-update ensemble-based data assimilation system.
The experiments are conducted using the Local Ensemble Transform Kalman filter implemented within the GSI-WRF data assimilation system.
The evaluation is performed using a case study approach involving a gigantic Mesoscale Convective System (MCS) developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.
On Nov, 22 a cold front crossed the center of Argentina triggering isolated convective cells that rapidly grew upscale into an exceptionally large MCS.
The MCS traveled approximately 2500 km from south to north, dissipating over Paraguay and Southern Brazil after 42 hours.
To the north of the region, a warm front contributed to the development of isolated multicells that ultimately grew and merged with the MSC.
The paper is organized as follows. The data assimilation system, the experimental design, and the observations used are presented in section 2. Results are discussed in section 3 and finally, conclusions are summarized in section 4.

@@

The model simulations for the case study are performed using the 3.9.1 version of the non-hydrostatic Advanced Research version of the Weather Research and Forecasting (WRF-ARW (V3.9), Skamarock et al. (2018)) model.
The resolution is 10 km (150 x 200 grid points) on the horizontal and 37 levels on the vertical with the top of the atmosphere at 50 hPa.
The initial and boundary conditions are provided by the Global Forecasting System (GFS) analysis (0.25\(^{\circ}\) horizontal resolution and 6-hour temporal resolution, National Centers for Environmental Prediction, National Weather Service, NOAA, U.S. Department of Commerce (2015)).
The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

The analyses are generated using the Local Ensemble Transform Kalman Filter (LETKF) implementation (V1.3, Hunt et al. (2007)) part of the Gridpoint Statistical Interpolation analysis system (GSI V3.8; Hu et al. (2018)).
A rapid update cycle approach is implemented with hourly analysis and a centered assimilation window, meaning that all the observations within \(\pm\) 30 minutes of the analysis time are assimilated.
Observations are assimilated in a 4D approach by comparing them with the corresponding first guess state at 10-minute intervals.
For radiance observations, the Community Radiative Transfer Model version 2.3 (CRTM; Han et al. (2006)) is used as an observation operator to calculate model-simulated brightness temperatures.

To reduce the effect of spurious correlations in the estimation of error covariances, we use a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) as in Dillon et al. (n.d.) for all types of observations.
A relaxation-to-prior inflation (Whitaker and Hamill, 2012) is applied with an inflation parameter \(\alpha=0.9\) to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

We use a 60-member ensemble where the ensemble mean at the beginning of the data assimilation cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle we used random perturbations to generate the initial ensemble perturbations. This method also helps to prevent an underestimation of the ensemble spread (Ouaraini et al., 2015). The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in Necker et al. (2020) and Maldonado et al. (2021). In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. These random perturbations are also applied at the boundaries to keep the ensemble spread within the domain.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/dominio-1} \caption{a) The horizontal domain used on the simulations (black box), the inner domain used for the experiment comparison (red box), the region shown in b) (light blue box) and the locations of Automatic Surface Weather Stations (ASWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles). b) Locations of radiosonde launches during the experiment, green dots corresponds to radiosondes launched during IOP 7, orange triangles are radiosondes launched during IOP 8 and purple square are radiosondes launched outside the IOP missions. The topography in meters is also shown (shaded).}\label{fig:dominio}
\end{figure}

@@

\hypertarget{conventional-and-satellite-derived-wind}{%
\subsubsection{Conventional and Satellite-derived wind}\label{conventional-and-satellite-derived-wind}}

The conventional and satellite-derived wind observations used are part of the Global Data Assimilation System (GDAS). We assimilated conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at National Centers for Environmental Prediction (NCEP) that consist of surface observations from 117 conventional surface weather stations (CSWS) and ships and upper-air observations from radiosondes and aircraft. The orange triangles in Figure \ref{fig:dominio} a), are the surface station locations included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for most radiosondes in the region. Wind surface observations over oceans (ASCATW) come from scaterometters and are also part of the PREPBUFR files.

Satellite-derived wind observations also come from GDAS and include information from GOES-16 (estimated from the visible, infrared, and water vapor channels) and METEOSAT 8 and 11 (visible and water vapor channels). Due to the domain covered by each of these satellites, GOES-16 is the primary source of satellite-derived winds (99 \% of the observations).

We used additional conventional observations from 866 Automatic Surface Weather Stations (ASWS) that are part of various public and private automatic station networks over Southern South America and are included in the RELAMPAGO Data Set repository (Garcia et al., 2019). These stations are indicated as green squares in Figure \ref{fig:dominio}a. They have higher spatial coverage than the CSWS and a sampling frequency of 10 minutes in most cases. The variables measured by the stations varied between networks; all stations measure temperature, but only 395 stations provide humidity, 422 provide pressure and 605 provide wind information.

Table \ref{tab:table-obs} lists all the observation types (i.e., pressure, temperature, specific humidity, and wind) available for each source, together with their associated errors. The observation errors were specified following the GSI default configuration. In some cases, the error varies with height and it depends on the specific platform (aircraft and satellite-derived wind). In terms of quality control, a gross check was performed by the observation operator by comparing the innovation (the difference between the observation and the model-simulated observation based on the first-guess) with a predefined threshold (also included in Table \ref{tab:table-obs}).

@@

\multirow{-4}{3.5em}{\raggedright\arraybackslash SFCSHP} & \multirow{-4}{4.5em}{\raggedright\arraybackslash Ships and Buoys} & Wind & 2.5 $ms^{-1}$ & 5 $ms^{-1}$\\
\cmidrule{1-5}
SATWND & Satellite-derived winds & Wind & 3.8-8 $ms^{-1*+}$ & 1.3-2.5 $ms^{-1+}$\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{*} Observation error varied with height.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{**} Observations over 600 hPa are rejected.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{+} Observation error depends on the report type.}\\
\end{tabular}
\end{table}

@@

Satellite radiances available through the GDAS data stream, consisting of infrared and microwave observations are used in this study. This includes the Advanced Microwave Sounding Unit - A (AMSU-A), Advanced Technology Microwave Sounder (ATMS), Microwave Humidity Sounder (MHS), High-resolution Infrared Radiation Sounder (HIRS/4), and 2 multispectral sensors, Atmospheric Infrared Sounder (AIRS) and Infrared Atmospheric Sounding Interferometer (IASI) over several satellite platforms (see Table 2). Since the regional domain is located in the mid-latitudes and the satellite platforms of interest are on polar orbits, each sensor scans the area only twice a day with a spatial coverage depending on the satellite swath. For this reason, the number of satellite observations varied significantly among cycles. This is evident in Figure 3 a) which shows the number of observations assimilated for RAD experiment (see Section \ref{exp}) at each analysis cycle. In particular, the multispectral sensors provided between 100 and 10.000 observations for every scan every 12 hours, contributing 82 \% of the total amount of assimilated radiances in our experiment. The vertical location of each radiance observation was estimated as the model level at which its weighting function was maximized as calculated by CRTM. The multispectral sensors have good vertical coverage and are able to sense from the lower troposphere and up to the lower stratosphere. The channels whose maximum weighting function is located in the stratosphere were rejected due to the low model top (50 hPa) used in the experiments.

The channels accepted for assimilation and their associated error were defined using the default GSI configuration. The data preprocessing, which is an essential step in the assimilation of radiances, was performed within the GSI system for each sensor specifically. Firstly a spatial data thinning is applied using a 60 km grid following (Jones et al., 2013; Lin et al., 2017; Singh et al., 2016), where the observations to be assimilated are chosen based on their distance to the model grid points, on the observation quality (based on available data quality information) and on the number of available channels (from the same pixel and sensor) that passed the quality control. Also, observations over the sea are preferred over those over land or snow (Hu et al., 2018).

The thinned observations were then bias corrected. The bias correction (BC) has an air-mass dependent and an angle-dependent component (Zhu et al., 2014) and it is calculated as a multi-linear function of N predictors \(p_i(x)\), with associated coefficients \(\beta_i\). Then, the bias corrected brightness temperature can be obtained as:

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis and First-guess},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a Mesoscale Convective System Case During RELAMPAGO. Part I: Impact on the Analysis and First-guess}
    \author[UBA,CIMA,CNRS]{Paola Belén Corrales\corref{1}}
   \ead{paola.corrales@cima.fcen.uba.ar} 
    \author[UBA,CIMA,CNRS]{Victoria Galligani}

@@

  \begin{abstract}
  In this paper, we evaluate the impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF over central and north-eastern Argentina where the surface and upper air observing networks are relatively coarse. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed during November 22, 2018. The accumulated precipitation associated with this MCS was quite high, exceeding 200 mm over northern Argentina and Paraguay. The MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during November 2018.

  We used the GSI-4DLETKF data assimilation package to produce analyses assimilating observations every hour with 10-km horizontal grid spacing and a 60-members multiphisics ensemble. We conducted four assimilation experiments using different sets of observations: CONV, consisting of conventional observations from NCEP's prepBUFR files, AWS combining CONV and dense automatic surface weather station networks, SATWND, combining AWS with satellite-derived winds and RAD, including SATWND and satellite radiances from different microwave and infrared sensors (AMSU, HIRS, MHS, ATMS, AIRS, and IASI). We found that the assimilation of observations with high temporal and spatial frequency generate an important impact on the PBL, primarily on the precipitable water content, that leads to the development of deep convection and heavy precipitation closer to the observed in this case study. The assimilation of radiance observations produces a better development of the convection mainly during the mature state of the MCS leading to an increase in the accumulated precipitation. We also run ensemble forecasts initialized from each experiment show and evaluated their skill to predict precipitation. We found that the assimilated observations in AWS, SATWND, and RAD helped to improve the precipitation forecast.
  \end{abstract}
   \begin{keyword} Regional Data Assimilation, Surface Obsevations, Satellite Observations\end{keyword}
 \end{frontmatter}

@@

Severe weather events cause significant human and material losses around the world. A large number of these phenomena are associated with the occurrence of deep moist convection including tornadoes, intense wind gusts, extreme precipitation in short time periods, large hail, and lightning.
Southern South America has been shown to have one of the highest frequencies in the world of favorable conditions for high-impact meteorological events (Brooks et al., 2003) and large hail events (Cecil and Blankenship, 2012), particularly during austral spring and summer.
This is also confirmed by observational evidence and high impact weather reports (Matsudo et al., 2015; Rasmussen et al., 2014). Recently, the RELAMPAGO-CACTI field campaign Nesbitt et al. (2021) has been conducted to investigate the mechanisms for convective initiation and the occurrence of high-impact weather events associated with deep convection in central Argentina.

Forecasting mesoscale meteorological phenomena and particularly deep moist convection is a scientific and technological challenge due to its limited predictability, and the difficulties in diagnosing the state of the atmosphere at small spatial and short temporal scales (for example from 1 to 10 kilometers and on the order of minutes). Mesoscale data assimilation (DA) is an approach that can provide appropriate initial conditions for the initialization of high-resolution forecasts (Sun et al., 2014) and thus has received increasing attention in the last decades.

For DA methods to be successful, observing networks with sufficient temporal and spatial resolution capable of capturing mesoscale variability should be used.

In that regard, Wheatley and Stensrud (2010) investigated the impact of assimilating surface pressure data in a mesoscale ensemble-based data assimilation system but found limited impact in two case studies related to mesoscale convective systems. Ha and Snyder (2014) showed that assimilating temperature and dew point temperature from high resolution surface weather station networks systematically improved the structure of the simulated planetary boundary layer and improved the short range precipitation forecast over the U.S. Chang et al. (2017), Bae and Min (2022) and Chen et al. (2016) reported beneficial effects of assimilating surface weather stations in a high resolution DA system using an ensemble Kalman filter, a 3-dimensional variational system and a 4-dimensional variational system respectively. Positive impacts have been found on the temperature and moisture forecast in the planetary boundary layer and in the location of precipitation systems. Sobash and Stensrud (2015) showed in a mesoscale ensemble based DA system that the positive impact upon convection initiation and the short range precipitation forecast is achieved if data is assimilated frequently (in the order of minutes, rather than in the order of hours). Maejima et al. (2019) investigated the impact of 1-minute frequency assimilation of surface observations using observation simulation experiments on a heavy rainfall case founding that assimilating high frequency and spatially dense observations lead to a better representation of mesoscale circulation even though the number of observations provided by surface stations is much less than the one provided by weather radars. Gasperoni et al. (2018) conducted a case study to evaluate the impact of assimilating observations produced by private weather stations which are not incorporated in the operational analysis. They found a positive effect of these observations upon the initiation of deep moist convection along a dryline. This result is particularly important for data sparse regions such as Southern South America, where operational networks are not dense enough to capture mesoscale details.

The impact of other types of high spatial and temporal resolution observations, such as atmospheric motion vectors (AMVs) has been investigated in the context of limited-area mesoscale data assimilation. Many studies have focused on the impact of these observations on the prediction of tropical storms (e.g.~Wu et al. (2014), Cherubini et al. (2006), and Sawada et al. (2019), among many others). Most of these studies reported an overall positive impact of the assimilation of AMVs for this type of storm. However, some works indicated mixed impacts (e.g.~Sawada et al. (2019) reported an improvement in the forecast of the track of the storm but a degradation in the forecasted intensity). As stated in J. Zhao et al. (2021a) and J. Zhao et al. (2021b), the impact of assimilating these data on high impact weather events associated with mid-latitude deep convection over land has received relatively less attention. J. Zhao et al. (2021a) and J. Zhao et al. (2021b) assimilated GOES-16 AMVs into a storm-scale three-dimensional variational DA system during three high impact weather events. They reported positive impacts of AMVs on the characterization of the storm environment and improved short range precipitation forecasts. Otsuka et al. (2015) and Mallick and Jones (2020) found a slight improvement in the short-range precipitation forecast due to the storm-scale assimilation of high frequency AMVs.

While the assimilation of radiance observations into global models is well established (), the direct assimilation of radiance data into regional models, however, still remains a challenge due to the sparse data coverage, the bias correction, and the relatively low top models used for this application. Bao et al. (2015) studied the impact of assimilating microwave and infrared radiance data on temperature and humidity forecasts over the western USA and found a reduction in the temperature bias at low and mid-levels as a result of the microwave observations but an opposite effect for infrared data. More recently, Zhu et al. (2019) studied the impact of assimilating satellite radiance data within a frequently updated regional system and showed an improvement for all variables, in particular for relative humidity at upper levels. Wang and Randriamampianina (2021) studied the impact of assimilating radiances in the high-resolution Copernicus European Regional Reanalysis. They reported that satellite radiance observations had a neutral impact on the analyses of geopotential height in the lower troposphere, while a slightly negative impact on the upper troposphere and the stratosphere. They also observed similar results for 3-h forecasts initialized from the analysis but a positive impact on the short-range forecasts (12 and 24 h). Given the mixed results, there is still room to analyze the utility of assimilating radiance observations in a limited-area DA system over land. Moreover, to the best of the author's knowledge, there are few to none studies related to the direct assimilation of radiance observations over South America.

In particular, in South America, the relatively scarcity of conventional observations such as radiosondes increases the potential impact of the observation sources previously discussed. Previous work has shown promising results of mesoscale DA in South America using some of the above mentioned data sources (e.g.~Dillon et al., 2016, 2021; gustavo Goncalves de Goncalves et al., 2015). In particular Dillon et al. (2021) assimilated high resolution surface weather station networks, GOES-16 AMVs, and satellite temperature and moisture retrievals with promising results. However, no work has been conducted yet over this region to investigate the potential contribution of the datasets discussed above.
The main objective of this work is to contribute to the quantification and comparison of the impact of high resolution surface weather stations, AMVs, and clear-sky satellite radiances, into a mesoscale, frequently-updated, and ensemble-based DA system. In particular, in this paper we will focus on the impact in the context of mid-latitude mesoscale convective system events. Another particular goal of this paper is to investigate the impact of these data sources in a region where the conventional observation network is rather sparse and where the potential contributions of these observing systems is larger.

To reach this goal, we conduct several DA experiments for a case study of a gigantic Mesoscale Convective System (MCS) that developed over Southern South America during Nov 22-23, 2018 during the intense observation period (IOP) of the RELAMPAGO field campaign.

The paper is organized as follows. The data assimilation system, the experimental design, and the observations used are presented in section 2. Results are discussed in section 3 and finally, conclusions are summarized in section 4.

@@

\hypertarget{case-study}{%
\subsection{Case Study}\label{case-study}}

On Nov 22, a cold front crossed the center of Argentina triggering isolated convective cells that rapidly grew upscale into an exceptionally large MCS.
The MCS traveled approximately 2500 km from south to north, dissipating over Paraguay and Southern Brazil after 42 hours.
To the north of the region, a warm front contributed to the development of isolated multicells that ultimately grew and merged with the MCS.

\hypertarget{data-assimilation-system-configuration}{%
\subsection{Data assimilation system configuration}\label{data-assimilation-system-configuration}}

The model simulations for the case study are performed using version 3.9.1 of the non-hydrostatic Advanced Research version of the Weather Research and Forecasting (WRF-ARW (V3.9), Skamarock et al. (2008)) model.
The horizontal grid spacing is 10 km (150 x 200 grid points) on the horizontal and 37 levels on the vertical with the top of the model at 50 hPa.
The initial and boundary conditions are provided by the Global Forecasting System (GFS) analysis (0.25\(^{\circ}\) horizontal grid spacing and 6-hour temporal resolution; National Centers for Environmental Prediction, National Weather Service, NOAA, U.S. Department of Commerce (2015)).
The domain covers the area indicated in Figure \ref{fig:dominio} to capture the development of the MCS during the simulated period.

The analyses are generated using the LETKF implementation (V1.3, Hunt et al. (2007)) part of the Gridpoint Statistical Interpolation analysis system (GSI V3.8; Shao et al. (2016)).
A rapid update cycle approach is implemented with hourly analysis and a centered assimilation window, meaning that all the observations within \(\pm\) 30 minutes of the analysis time are assimilated.
Observations are assimilated in a 4D approach by comparing them with the corresponding first guess state at 10-minute intervals.
For radiance observations, the Community Radiative Transfer Model version 2.3 (CRTM; Han et al. (2006)) is used as an observation operator to calculate model-simulated brightness temperatures. In addition to being already coupled to the GSI system.

We use a 60-member ensemble where the ensemble mean at the beginning of the DA cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle we used random perturbations to generate the initial ensemble perturbations. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5\(^{\circ}\) horizontal grid spacing with a smooth time evolution as in Necker et al. (2020) and Maldonado et al. (2021). In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. This method helps to prevent an underestimation of the ensemble spread (Ouaraini et al., 2015), and the random perturbations are also applied at the boundaries to maintain proper levels of ensemble spread within the domain.

@@

To reduce the effect of spurious correlations in the estimation of error covariances, we use a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) as in Dillon et al. (2021) for all types of observations.
A relaxation-to-prior inflation (Whitaker and Hamill, 2012) is applied with an inflation parameter \(\alpha=0.9\) to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

\begin{figure}
\includegraphics[width=1\linewidth]{../figures/dominio-1} \caption{a) The domain used for the simulations (black box), the inner domain used for the experiment comparison (red box), the region shown in b) (light blue box) and the locations of Automatic Surface Weather Stations (AWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles). b) Locations of radiosonde launches during the RELAMPAGO. Green dots correspond to radiosondes launched during IOP 7, orange triangles are radiosondes launched during IOP 8, and purple squares are radiosondes launched outside the IOP missions. The topography in meters is also shown (shaded).}\label{fig:dominio}
\end{figure}

@@

\hypertarget{conventional}{%
\subsubsection{Conventional}\label{conventional}}

The conventional observations used are part of the Global Data Assimilation System (GDAS) data stream. We assimilated conventional observations included in the Binary Universal Form for Representation of Meteorological Data (PREPBUFR) files generated at the National Centers for Environmental Prediction (NCEP). These consist of surface observations from 117 Conventional Surface Weather Stations (CSWS), ships, and upper-air observations from 13 radiosondes sites and aircraft. The orange triangles in Figure \ref{fig:dominio} indicate the location of the surface station included in this experiment. The frequency of these observations varied between 1 hour for surface stations and 12/24 hours for radiosondes. Wind surface observations over oceans (ASCATW) come from scatterometers and are also included in the PREPBUFR files.

Table \ref{tab:table-obs} lists all the observation types (i.e., surface pressure, temperature, specific humidity, and wind) available for each source, together with their associated errors. The observation errors were specified following the GSI default configuration. In some cases, the error varies with height and depends on the specific platform (aircraft and satellite-derived wind). In terms of quality control, a gross check was performed by the observation operator by comparing the innovation (the difference between the observation and the model-simulated observation based on the first-guess) with a predefined threshold that depends on the observation error (also included in Table \ref{tab:table-obs}).

\hypertarget{aws-networks}{%
\subsubsection{AWS networks}\label{aws-networks}}

We also assimilate data from 866 Automatic Weather Stations (AWS) that are part of 17 public and private surface networks over Southern South America. The dataset used in this study has been obtained at the RELAMPAGO Data Set repository (Garcia et al., 2019). These stations are indicated as green squares in Figure \ref{fig:dominio}a. They have higher spatial coverage than the CSWS and a sampling frequency of 10 minutes in most cases. All stations measure temperature, but only 395 stations provide humidity, 422 provide pressure and 605 provide wind information.
Observation errors used to assimilate these observations are the same as for the CSWS (see Table \ref{tab:table-obs})

\hypertarget{satellite-derived-winds}{%
\subsubsection{Satellite derived winds}\label{satellite-derived-winds}}

Satellite-derived wind observations are also included in the PREPBUFR files available every 6 hs, and consist of estimations from GOES-16 (using the visible, infrared, and water vapor channels) and METEOSAT 8 and 11 (using the visible and water vapor channels). Due to the domain covered by each of these satellites, GOES-16 is the primary source of satellite-derived winds (99 \% of the observations). Observation errors used to assimilate these observations are indicated in Table \ref{tab:table-obs}.

@@

\multirow{-4}{3.5em}{\raggedright\arraybackslash SFCSHP} & \multirow{-4}{4.5em}{\raggedright\arraybackslash Ships and Buoys} & Wind & 2.5 $ms^{-1}$ & 5 $ms^{-1}$\\
\cmidrule{1-5}
SATWND & Satellite-derived winds & Wind & 3.8-8 $ms^{-1*+}$ & 1.3-2.5 $ms^{-1+}$\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{*} Observation error varied with height.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{**} Observations above 600 hPa are rejected.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{+} Observation error depends on the report type.}\\
\end{tabular}
\end{table}

@@

Satellite radiances available through the GDAS data stream, consisting of infrared and microwave observations are used in this study. This includes the Advanced Microwave Sounding Unit - A (AMSU-A), Microwave Humidity Sounder (MHS), and 2 multispectral sensors; the Atmospheric Infrared Sounder (AIRS) and the Infrared Atmospheric Sounding Interferometer (IASI) over several satellite platforms (see Table 2). Since the regional domain is located in the mid-latitudes and the satellite platforms of interest are on polar orbits, each sensor scans the area only twice a day with a spatial coverage depending on the satellite swath. For this reason, the number of satellite observations varied significantly among cycles. In particular, the multispectral sensors provided between 100 and 1000 observations for every scan every 12 hours, contributing 88 \% of the total amount of assimilated radiances in our experiment. The vertical location of each radiance observation was estimated as the model level at which its weighting function was maximized as calculated by CRTM. The multispectral sensors have good vertical coverage and are able to sense from the lower troposphere and up to the lower stratosphere.
The channels accepted for assimilation and their associated errors were defined taking into account the low model top (50 hPa). The data preprocessing, which is an essential step in the assimilation of radiances, was performed within the GSI system for each sensor specifically. Firstly a spatial data thinning is applied using a 60 km grid following (Jones et al., 2013; Lin et al., 2017; Singh et al., 2016), where the observations to be assimilated are chosen based on their distance to the model grid points, the observation quality (based on available data quality information), and the number of available channels (from the same pixel and sensor) that passed the quality control. Also, observations over the sea are preferred to those over land or snow (Hu et al., 2018).

The thinned observations were then bias corrected. The bias correction (BC) has an air-mass dependent and an angle-dependent component (Zhu et al., 2014) and it is calculated as a multi-linear function of N predictors \(p_i(x)\), with associated coefficients \(\beta_i\). Then, the bias corrected brightness temperature (BT\_\{bc\}) can be obtained as:
